NFC and burnout in teachers - A replication and extension study

### 2022-02-21 Manuscript/Manuscript.Rmd
split Rmd into Analysis and Manuscript

  # define required packages

  packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lavaan", "psych", "MVN", "MBESS",
               "kableExtra", "Hmisc", "semPlot", "ggplot2", "knitr", "qgraph", "ppcor", "stats", "apa", "GGally")

  # check whether each package is installed and install and/or load library

  installed_packages <- packages %in% rownames(installed.packages())
  if (any(installed_packages == FALSE)) {
    install.packages(packages[!installed_packages])
  }
  invisible(lapply(packages, library, character.only = TRUE))

```{r analysispreferences, echo=FALSE, message=FALSE, warning=FALSE}

  # Seed for random number generation
  set.seed(13)
  knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

  # Set a number for the bootstrapping procedures
  bootnum <- 5000

@@

```{r import, echo=FALSE, message=FALSE, warning=FALSE}
  # Define the top level as the one where this file lies
  # If the rest of the files follow the structure of the Github repository, everything will work
  # (Simply download the entire repository to any location on your computer)

  # Load the data file

  load(here("Data", "data.Rda"))

  # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
  consistencies <- read_rds(here("Data", "consistencies.rds"))
  outlierconsistencies <- read_rds(here("Data", "outlierconsistencies.rds"))

  # create a vector of consistencies to be used as the diagonal in a table later
  consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
                        format(round(t(consistencies[5,2:11]), digits = 2), nsmall = 2), rep(")",10))
  # paste together to create the output "alpha(omega)"
  consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")

@@

```{r splitandrecode, echo=FALSE, message=FALSE, warning=FALSE}

  # Put questionnaire data into different data frames for easy access

  mbi <- data[,grep("MBI", colnames(data))]   # Maslach Burnout Inventory
  erq <- data[,grep("ERQ", colnames(data))]   # Emotion Regulation Questionnaire
  scs <- data[,grep("SCS", colnames(data))]   # Self Control Scale
  ws <- data[,grep("WS", colnames(data))]     # Work Satisfaction
  ncs <- data[,grep("NCS", colnames(data))]   # Need for Cognition Scale
  ncs <- ncs[,-9]                             # remove the dummy item
  covb <- data[,grep("COV", colnames(data))]  # Covid Burden Items
  dth <- ws[,c(4,8,9)]                        # the Work Satisfaction items for the latent variable Demands Too High
  dtl <- ws[,c(12,26,27)]                     # the Work Satisfaction items for the latent variable Demands Too Low
  drf <- ws[,c(17,21,24)]                     # the Work Satisfaction items for the latent variable Demand-Resource-Fit

  # Create a list with keys for the questionnaire subscales/latent variables/item parcels

  keylist <- list(mbi_ee = c(5,7,10,11,14,18,19,20,21), mbi_dp = c(1,6,9,15,17), mbi_rpe = c(2,3,4,8,12,13,16),
                  erq_supp = c(2,4,6,9), erq_reap = c(1,3,5,7,8,10),
                  scs = c(2,3,4,5,6,7,8,10,11),
                  ncs = c(4,6,7,8,9,10,11,12,15,16),
                  ws = c(4,5,6,8,9,10,11,13,16,19,20,33))

  # Recode all the reverse coded items

  mbi[,keylist$mbi_rpe] <- 7 - mbi[,keylist$mbi_rpe]  # Recode from 1-6 to 6-1
  scs[,keylist$scs] <- 6 - scs[,keylist$scs]          # Recode from 1-5 to 5-1
  scs <- scs - 3                                      # Recode all from 1-5 to -2-+2
  ncs[,keylist$ncs] <- 8 - ncs[,keylist$ncs]          # Recode from 1-7 to 7-1
  ncs <- ncs - 4                                      # Recode all from 1-7 to -3-+3
  ws[,keylist$ws] <- 6 - ws[,keylist$ws]              # Recode from 1-5 to 5-1
  ws <- ws - 3                                        # Recode all from 1-5 to -2-+2
  covb[,c(2,3,4,9)] <- 4 - covb[,c(2,3,4,9)]          # Recode from 1-3 to 3-1
  covb[,8] <- 3 - covb[,8]                            # Recode from 1-2 to 2-1
  # The following recoding is opposite to what is described in the methods section of the paper, which
  # is due to the fact that the questionnaire is originally coded as 1 (false) to 5 (true), but it was
  # coded as 1 (true) to 5 (false) in the SoSciSurvey of the present study.
  dth <- 6 - dth                                      # Recode all from 1-5 to 5-1
  dth <- dth - 3                                      # Recode all from 1-5 to -2-+2
  dtl <- dtl - 3                                      # Recode all from 1-5 to -2-+2
  drf <- 6 - drf                                      # Recode all from 1-5 to 5-1
  drf <- drf -3                                       # Recode all from 1-5 to -2-+2

```{r parcelling, echo=FALSE, message=FALSE, warning=FALSE}

  # Parcelling preparation: Compute factor loadings on the first PCA component

  ncs_pca <- princomp(ncs, cor = FALSE, scores = TRUE)
  ncs_load <- ncs_pca$loadings[,1]

  # Parcelling function

  parcel.gen <- function(loadings, parcels = 4,seed = 242,iterations = 10000) {

    p = parcels                   # number of parcels
    l = length(loadings)          # number of items
    set.seed(seed)              # seed for reproducibility

    out = parcels = NULL            # set up containers
    for (k in 1:iterations) {

      s = sample(1:l,l,replace = F) # random item order
      m = matrix(s,ncol = 4)        # separate into parcels

      # temporarily convert item numbers per parcel to concatenated strings
      parcels.i = NULL
      for (i in 1:p) {
        parcels.i = c(parcels.i,paste0(sort(m[,i]),collapse = ","))
      }
      # write to container
      parcels = rbind(parcels,parcels.i)

      # compute average item loadings per parcel
      avg.h = colMeans(matrix(loadings[m],ncol = 4))

      # compute differences between all average item loadings
      h.diff = NULL
      for (i in 1:(p-1)) {
        for (j in (i+1):p) {
          h.diff = c(h.diff,abs(avg.h[i]-avg.h[j]))
        }
      }

      # sum up differences
      h.diff.sum = sum(h.diff)
      # write summed differences to container
      out = c(out,h.diff.sum)
    }

    # find minimum summed difference and generate matrix or respective items
    final.parcels = matrix(as.numeric(unlist(strsplit(parcels[which.min(out),],','))),ncol = 4)
    # obtain corresponding loadings per parcel
    final.h = matrix(loadings[final.parcels],ncol = 4)

    # return result as list
    return(list(items = final.parcels,loadings = final.h,avg.loadings = colMeans(final.h),summed.difference = min(out)))

  }

  ncs_parcels <- parcel.gen(loadings = ncs_load) # execute function

  # Add parcelling result to the key list

  keylist <- c(keylist, parcel1 = list(ncs_parcels$items[,1]), parcel2 = list(ncs_parcels$items[,2]),
               parcel3 = list(ncs_parcels$items[,3]), parcel4 = list(ncs_parcels$items[,4]))
```

```{r scores, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}

# Create data frame to feed the values of every subject into

  score_data <- data.frame(id = c(1:180),
                           years = data$yearsteaching,
                           mbi = rep(0,180),
                           mbi_ee = rep(0,180), mbi_dp = rep(0,180), mbi_rpe = rep(0,180),
                           erq = rep(0,180),
                           erq_supp = rep(0,180), erq_reap = rep(0,180),
                           scs = rep(0,180),
                           ncs = rep(0,180),
                           nfc1 = rep(0,180), nfc2 = rep(0,180), nfc3 = rep(0,180), nfc4 = rep(0,180),
                           dth = rep(0,180),
                           dth1 = rep(0,180), dth2 = rep(0,180), dth3 = rep(0,180),
                           dtl = rep(0,180),
                           dtl1 = rep(0,180), dtl2 = rep(0,180), dtl3 = rep(0,180),
                           drf = rep(0,180),
                           drf1 = rep(0,180), drf2 = rep(0,180), drf3 = rep(0,180),
                           covb = rep(0,180))

  # Compute individual scores or (for the latent variable indicators) feed in raw values

  for (i in 1:nrow(data)) {
    score_data[i,c(3:ncol(score_data))] <- c(rowSums(mbi[i,]),
                                             rowSums(mbi[i,keylist$mbi_ee]), rowSums(mbi[i,keylist$mbi_dp]), rowSums(mbi[i,keylist$mbi_rpe]),
                                             rowSums(erq[i,]),
                                             rowSums(erq[i,keylist$erq_supp]), rowSums(erq[i,keylist$erq_reap]),
                                             rowSums(scs[i,]),
                                             rowSums(ncs[i,]),
                                             rowSums(ncs[i,keylist$parcel1]), rowSums(ncs[i,keylist$parcel2]), rowSums(ncs[i,keylist$parcel3]), rowSums(ncs[i,keylist$parcel4]),
                                             rowSums(dth[i,]),
                                             dth[i,1], dth[i,2], dth[i,3],
                                             rowSums(dtl[i,]),
                                             dtl[i,1], dtl[i,2], dtl[i,3],
                                             rowSums(drf[i,]),
                                             drf[i,1], drf[i,2], drf[i,3],
                                             rowSums(covb[i,]))
  }

  # This function was taken from an answer on a Stackoverflow question on August 30th 2021
  # https://stackoverflow.com/questions/35085261/how-to-use-loess-method-in-ggallyggpairs-using-wrap-function/35088740

  my_fn <- function(data, mapping, pts=list(), smt=list(), ...){
    ggplot(data = data, mapping = mapping, ...) +
      do.call(geom_point, pts) +
      do.call(geom_smooth, smt)
  }

  # Plot a big correlational matrix to check for non-linear associations and unexpected outliers
  multicorrplot <- ggpairs(score_data[,c("years","mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                         "scs","ncs","dth","dtl","drf","covb")], lower = list(continuous = my_fn))

  # It looked like there was an outlier in the data, especially visible in the MBI data
  # Check for the outlier in particular, using the data involved in the mediation
  outlierplot <- outlier(score_data[ ,c(6,8:11)], plot = TRUE)

  # Remove participant 161 in a second version of the data frame (for the supplementary material analysis)
  score_data_no_outlier <- score_data[score_data$mbi < 100, ]

```{r descriptives, echo=FALSE, message=FALSE, warning=FALSE}

  # Tests for normal distribution

    # using Mardia's test for multivariate normal distribution
    # results will be fed into the desc_met data frame in the next step

    isnorm_test <- mvn(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")],
                       mvnTest = "mardia", covariance = TRUE, desc = TRUE, univariateTest = "SW")

  # Descriptive statistics

    # Categorical descriptives: data frame with percentages of responses per category

    desc_cat <- data.frame(answer = c(1,2,3,4,5),
                           age = c(nrow(data[data$age == 1,])/nrow(data), nrow(data[data$age == 2,])/nrow(data), nrow(data[data$age == 3,])/nrow(data),
                                   nrow(data[data$age == 4,])/nrow(data), nrow(data[data$age == 5,])/nrow(data)),
                           gender = c(nrow(data[data$gender == 1,])/nrow(data), nrow(data[data$gender == 2,])/nrow(data), nrow(data[data$gender == 3,])/nrow(data),0,0),
                           schooltype = c(nrow(data[data$schooltype == 1,])/nrow(data), nrow(data[data$schooltype == 2,])/nrow(data), nrow(data[data$schooltype == 3,])/nrow(data),
                                          nrow(data[data$schooltype == 4,])/nrow(data), nrow(data[data$schooltype == 5,])/nrow(data)))

    # Metric descriptives: data frame with descriptive values of questionnaires

    desc_met <- data.frame(Variable = c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","DTH","DTL","DRF","COV"),
                           Minimum = sapply(score_data[,c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")], min),
                           Maximum = sapply(score_data[,c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap","scs","ncs","dth","dtl","drf","covb")], max),
                           Mean = isnorm_test$Descriptives$Mean,
                           SD = isnorm_test$Descriptives$Std.Dev,
                           Normality = isnorm_test$univariateNormality$Normality,
                           Skewness = isnorm_test$Descriptives$Skew,
                           Kurtosis = isnorm_test$Descriptives$Kurtosis)
    # Drop the row names

    rownames(desc_met) <- NULL

    # Replace the capital YESes and NOs with small ones

    desc_met$Normality[grep("NO", desc_met$Normality)] <- "No"
    desc_met$Normality[grep("YES", desc_met$Normality)] <- "Yes"

    # Round the values

    desc_met[ ,c("Mean","SD","Skewness","Kurtosis")] <- round(desc_met[ ,c("Mean","SD","Skewness","Kurtosis")], digits = 2)

    # Put the information in a table

    desc_table <-
      kbl(desc_met,
          caption = "Descriptive statistics of the questionnaire scores.",
          booktabs = T, # no vertical lines
          escape = F, # correctly print special characters
          align = c("l",rep("r",7))) %>% # right aligns the text in every column except for the first
      kable_styling(latex_options = c("striped", "scale_down")) %>%
      footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation. \\\\textit{N} = 180.",
               escape = F, # correctly print special characters
               threeparttable = T) # line breaks in the footnote

```{r consistency, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE}

  # Tests for internal consistency

    # Create data frame to feed values into

    consistencies <- data.frame(value = c("lower CI alpha","raw alpha","upper CI alpha",
                                          "lower CI omega","raw omega","upper CI omega"))

    # Compute Cronbach's Alpha and MacDonald's Omega for questionnaires and demand-resource-ratios

    set.seed(13) # seed for reproducing the bootstrapping

    # Maslach Burnout Inventory

    cronalph <- alpha(mbi, check.keys = TRUE)
    macomega <- ci.reliability(data=mbi, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$mbi <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # MBI emotional exhaustion

    cronalph <- alpha(subset(mbi, select = keylist$mbi_ee), check.keys = TRUE)
    macomega <- ci.reliability(data=subset(mbi, select = keylist$mbi_ee), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$mbi_ee <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # MBI depersonalization

    cronalph <- alpha(subset(mbi, select = keylist$mbi_dp), check.keys = TRUE)
    macomega <- ci.reliability(data=subset(mbi, select = keylist$mbi_dp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$mbi_dp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # MBI reduced personal efficacy

    cronalph <- alpha(subset(mbi, select = keylist$mbi_rpe), check.keys = TRUE)
    macomega <- ci.reliability(data=subset(mbi, select = keylist$mbi_rpe), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$mbi_rpe <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                 cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                 macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # ERQ

    cronalph <- alpha(erq, check.keys = TRUE)
    macomega <- ci.reliability(data=erq, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$erq <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # ERQ suppression

    cronalph <- alpha(subset(erq, select = keylist$erq_supp), check.keys = TRUE)
    macomega <- ci.reliability(data=subset(erq, select = keylist$erq_supp), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$erq_supp <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # ERQ reappraisal

    cronalph <- alpha(subset(erq, select = keylist$erq_reap), check.keys = TRUE)
    macomega <- ci.reliability(data=subset(erq, select = keylist$erq_reap), type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$erq_reap <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                                  cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                                  macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Self Control Scale

    cronalph <- alpha(scs, check.keys = TRUE)
    macomega <- ci.reliability(data=scs, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$scs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Need for Cognition Scale

    cronalph <- alpha(ncs, check.keys = TRUE)
    macomega <- ci.reliability(data=ncs, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$ncs <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Covid burden

    cronalph <- alpha(covb, check.keys = TRUE)
    macomega <- ci.reliability(data=covb, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$covb <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Demands Too High

    cronalph <- alpha(dth, check.keys = FALSE)
    macomega <- ci.reliability(data=dth, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$dth <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Demands Too Low

    cronalph <- alpha(dtl, check.keys = FALSE)
    macomega <- ci.reliability(data=dtl, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$dtl <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    # Demand Resource Fit

    cronalph <- alpha(drf, check.keys = FALSE)
    macomega <- ci.reliability(data=drf, type="omega", conf.level = 0.95, interval.type="bca", B=bootnum)
    consistencies$drf <- round(c(cronalph$total$raw_alpha - 1.96 * cronalph$total$ase, cronalph$total$raw_alpha,
                             cronalph$total$raw_alpha + 1.96 * cronalph$total$ase,
                             macomega$ci.lower, macomega$est, macomega$ci.upper), digits = 2)

    remove(cronalph,macomega) # delete the temporary variable

```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}

    # The following function for nicely formatted correlation output was taken from
    # https://paulvanderlaken.com/2020/07/28/publication-ready-correlation-matrix-significance-r/
    # on the 5th of August 2021

    correlation_matrix <- function(df,
                                   type = "spearman",
                                   digits = 3,
                                   decimal.mark = ".",
                                   use = "all",
                                   show_significance = TRUE,
                                   replace_diagonal = FALSE,
                                   replacement = ""){
      # check arguments
      stopifnot({
        is.numeric(digits)
        digits >= 0
        use %in% c("all", "upper", "lower")
        is.logical(replace_diagonal)
        is.logical(show_significance)
        is.character(replacement)
      })
      # we need the Hmisc package for this
      require(Hmisc)

      # retain only numeric and boolean columns
      isNumericOrBoolean = vapply(df, function(x) is.numeric(x) | is.logical(x), logical(1))
      if (sum(!isNumericOrBoolean) > 0) {
        cat('Dropping non-numeric/-boolean column(s):', paste(names(isNumericOrBoolean)[!isNumericOrBoolean], collapse = ', '), '\n\n')
      }
      df = df[isNumericOrBoolean]

      # transform input data frame to matrix
      x <- as.matrix(df)

      # run correlation analysis using Hmisc package
      correlation_matrix <- Hmisc::rcorr(x, type = type)
      R <- correlation_matrix$r # Matrix of correlation coeficients
      p <- correlation_matrix$P # Matrix of p-value

      # transform correlations to specific character format
      Rformatted = formatC(R, format = 'f', digits = digits, decimal.mark = decimal.mark)

      # if there are any negative numbers, we want to put a space before the positives to align all
      if (sum(!is.na(R) & R < 0) > 0) {
        Rformatted = ifelse(!is.na(R) & R > 0, paste0(" ", Rformatted), Rformatted)
      }

      # add significance levels if desired
      if (show_significance) {
        # define notions for significance levels; spacing is important.
        stars <- ifelse(is.na(p), "", ifelse(p < .001, "***", ifelse(p < .01, "**", ifelse(p < .05, "*", ""))))
        Rformatted = paste0(Rformatted, stars)
      }

      # make all character strings equally long
      max_length = max(nchar(Rformatted))
      Rformatted = vapply(Rformatted, function(x) {
        current_length = nchar(x)
        difference = max_length - current_length
        return(paste0(x, paste(rep(" ", difference), collapse = ''), sep = ''))
      }, FUN.VALUE = character(1))

      # build a new matrix that includes the formatted correlations and their significance stars
      Rnew <- matrix(Rformatted, ncol = ncol(x))
      rownames(Rnew) <- colnames(Rnew) <- colnames(x)

      # replace undesired values
      if (use == 'upper') {
        Rnew[lower.tri(Rnew, diag = replace_diagonal)] <- replacement
      } else if (use == 'lower') {
        Rnew[upper.tri(Rnew, diag = replace_diagonal)] <- replacement
      } else if (replace_diagonal) {
        diag(Rnew) <- replacement
      }

      return(Rnew)
    }

    # correlate variables
    correlations <- correlation_matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                                    "scs","ncs","dth","dtl","drf","covb")],
                                       type = "spearman",
                                       use = "lower",
                                       show_significance = FALSE,
                                       replace_diagonal = TRUE,
                                       replacement = "")

    # reorder the columns of the consistencies data frame to match the correlation columns
    consist_diag <- consistencies[c(colnames(correlations))]

    # create a vector of consistencies to be used as the diagonal in a table later
    consist_diag <- cbind(format(round(t(consist_diag[2,]), digits = 2), nsmall = 2), rep("(",10),
                          format(round(t(consist_diag[5,]), digits = 2), nsmall = 2), rep(")",10))

    # paste together to create the output "alpha(omega)"
    consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")

    # add previously assembled diagonal with alpha and omega values
    diag(correlations) <- consist_diag

    # set row and column names for better table printing
    row.names(correlations) <- c("1. MBI","2. MBI EE","3. MBI DP","4. MBI RPE","5. ERQ","6. ERQ S","7. ERQ R",
                                 "8. SCS","9. NFC","10. DTH","11. DTL","12. DRF","13. COV")
    colnames(correlations) <- c("1","2","3","4","5","6","7","8","9","10","11","12","13")

    # create array with p-values of correlation coefficients
    corr_pvalues <- rcorr(as.matrix(score_data[c("mbi","mbi_ee","mbi_dp","mbi_rpe","erq","erq_supp","erq_reap",
                                                 "scs","ncs","dth","dtl","drf","covb")]), type = "spearman")$P
    # replace upper triangle with NA
    corr_pvalues[upper.tri(corr_pvalues, diag = TRUE)] <- NA

    # replace p-values with asterisks depending on significance level
    corr_pvalues <- ifelse(is.na(corr_pvalues), "", ifelse(corr_pvalues < .001, "***", ifelse(corr_pvalues < .01, "**", ifelse(corr_pvalues < .05, "*", ""))))

    # convert to matrix for the paste()-function
    correlations <- as.matrix(correlations)
    corr_pvalues <- as.matrix(corr_pvalues)

    # paste correlations and asterisks together
    correlations <- matrix(paste(correlations, corr_pvalues, sep = ""),
                           nrow = nrow(correlations), dimnames = dimnames(correlations))

@@

@@

  corr_table <-
  kbl(correlations,
      caption = "Spearman correlations and internal consistencies of the questionnaire scores.",
      booktabs = TRUE, # no vertical lines
      escape = FALSE, # correctly print special characters
      align = rep("l",14)) %>% # left aligns the text in every column
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden. \\\\textit{N} = 180. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = FALSE, # correctly print special characters
             threeparttable = TRUE) %>% # line breaks in the footnote
  kableExtra::landscape() # make the table horizontal

@@

```{r objective1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}

  # Replication of Grass et al. (2018)

  repli_model <- '
  # direct paths
    scs       ~   a1 * ncs
    erq_reap  ~   a2 * ncs
    erq_supp  ~   a3 * ncs
    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs

  # indirect effects
    Indirect1 := a1 * b1
    Indirect2 := a2 * b2
    Indirect3 := a3 * b3

  # contrast (if significant, the effects differ)
    Contrast := Indirect1 - Indirect2 - Indirect3

  # total effect
    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3)
'

  # Determine the model fit

  fit <- sem(
    model = repli_model,
    data  = score_data,
    se = "bootstrap",
    bootstrap = 2000
  )

  # Get summary

  fit_summ <- summary(fit, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
          estimates = TRUE, ci = TRUE)
```

@@

  # put relevant data from the mediation into a table for reporting

  # put data into data frame

  replic_table <- data.frame("Path" = c("NFC on Self Control", "NFC on Reappraisal", "NFC on Suppression",
                                   "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
                                   "NFC on RPE via Self Control", "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
                                   "Total Effect"),
                          "$B$" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit_summ$PE$std.all[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

  # format the numbers to three digits after the decimal point

  replic_table[2:ncol(replic_table)] <- format(round(replic_table[2:ncol(replic_table)], digits = 3), nsmall = 2)

@@

```{r objective1years, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}

  # Replication of Grass et al. (2018) using years spent teaching as a variable influencing self-control
  # (as indicated by the correlation of it with SCS but not with the other variables)

  repli_model_years <- '
  # direct paths
    scs       ~   a1 * ncs + y * years
    erq_reap  ~   a2 * ncs
    erq_supp  ~   a3 * ncs
    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs

  # indirect effects
    Indirect1 := (a1 * b1) + (y * b1)
    Indirect2 := a2 * b2
    Indirect3 := a3 * b3

  # contrast (if significant, the effects differ)
    Contrast := Indirect1 - Indirect2 - Indirect3

  # total effect
    Total := c + (a1 * b1) + (a2 * b2) + (a3 * b3) + (y * b1)
'

  # Determine the model fit

  fityears <- sem(
    model = repli_model_years,
    data  = score_data,
    se = "bootstrap",
    bootstrap = 2000
  )

  # Get summary

  fityears_summ <- summary(fityears, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
          estimates = TRUE, ci = TRUE)
```

@@

```{r objective2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}

  # SEM with demand-resource-ratios

>>>>

  # load libraries

  library(bibtex)       # for referencing, "bibtex" package
  library(here)         # for path independent file referencing, "here" package
  library(papaja)       # APA conform output, "papaja" package
  library(kableExtra)   # for great tables in R Markdown, "kableExtra" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(GGally)       # for plotting, "GGally" package
  library(semPlot)      # for plotting, "semPlot" package
  library(knitr)        # for including plots and such, "knitr" package
  library(apa)          # APA conform output, "apa" package
  library(effectsize)   # for effect sizes and CIs, "effectsize" package

  # set top level directory to source file

  # load the workspace variables that have been computed with the Analysis.R script

  load(here("Data","Workspace.RData"))

@@

@@

@@

```{r cdescriptivestable, echo=FALSE, message=FALSE, warning=FALSE, caption="Descriptive statistics of the questionnaire scores."}
  desc_table <-
      kbl(desc_met,
          caption = "Descriptive statistics of the questionnaire scores.",
          booktabs = T, # no vertical lines
          escape = F, # correctly print special characters
          align = c("l",rep("r",7))) %>% # right aligns the text in every column except for the first
      kable_styling(latex_options = c("striped", "scale_down")) %>%
      footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden, SD = Standard deviation. \\\\textit{N} = 180.",
               escape = F, # correctly print special characters
               threeparttable = T) # line breaks in the footnote
```

@@

  corr_table <-
  kable(correlations,
      caption = "Spearman correlations and internal consistencies of the questionnaire scores.",
      booktabs = TRUE, # no vertical lines
      escape = FALSE, # correctly print special characters
      align = rep("l",14)) %>% # left aligns the text in every column
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden. \\\\textit{N} = 180. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = FALSE, # correctly print special characters
             threeparttable = TRUE) %>% # line breaks in the footnote
  kableExtra::landscape() # make the table horizontal

@@

@@

@@

@@

```{r objective2table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the demand-resource-ratio model."}
